---
title: "JR birthday"
author: "Jen Richmond"
date: "13/07/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```


#Memes

## Option 1: memer 

The memer package by [Sam Tyner](https://github.com/sctyner/memer) allows you to replace text in popular memes with your own. 

### install the package

```{r eval=FALSE}
devtools::install_github("sctyner/memer")
```

### load the package, get a list of available memes

```{r}
library(memer)
meme_list()
```

### choose a meme
```{r}

meme_get("OprahGiveaway") 

```

### replace the text with your own
```{r}
meme_get("OprahGiveaway") %>%
  meme_text_bottom("Happy Birthday \n R-Ladies Sydney!")
```

Some memes have more than 1 text field

```{r}
meme_get("TrumpBillSigning") %>% meme_text_trump("R-Ladies Sydney", "Happy Birthday")
```

##Option 2: meme

[meme package](https://github.com/GuangchuangYu/meme/)

[Vignette](https://cran.r-project.org/web/packages/meme/vignettes/meme.html)

### install package
```{r eval = FALSE}
devtools::install_github("GuangchuangYu/meme")
```

### load the package

```{r}
library(meme)
```

ALso need sysfonts package. Ran into problems, fixed on my Mac by installing XQuartz. See [issue here](https://github.com/GuangchuangYu/hexSticker/issues/18)

Load an image
```{r}
#vignette example
pic1 <- system.file("success.jpg", package="meme")
 
```
Add the text
```{r}
meme(pic1, "code", "all the things!")
```

Choose ANY image

```{r}
meme("kitten.jpg", "am i in your way?") %>%
  meme_save("kitty.jpg")

```

#Option 3: memery 

https://github.com/leonawicz/memery

This is a shiny app based meme maker. [Vignette here](https://cran.r-project.org/web/packages/memery/vignettes/memery.html). 


magick package is recommended

### install the package
```{r}
install.packages("memery")
```

### load the package and shiny app

```{r}
library(memery)

```

Define a pic and txt, then the meme function overlays txt on pic and saves to jpg. Can get pic from your machine or the web 
```{r}
#load pic from package 
pic <- system.file("philosoraptor.jpg", package = "memery")
#make list of txt possibilities
txt <- c("What to call my R package?", "Perhaps...")

#overlay txt option 1 on pic and save to jpg
meme(pic, txt[1], "meme1.jpg")

```

```{r}
#get image from the web
web <- "https://imgflip.com/s/meme/Philosoraptor.jpg"
#overlay txt option 2 on the web image
meme(web, txt[2], "meme2.png")
```

```{r}
#define new txt possibilities

txt2 <- c("Are you sure you need to work?", "Am I in your way?")
# overlay top and bottom option on kitten image =, save to jpg
meme("kitten.jpg", txt2, "kitty2.jpg")

clrs <- c("orange", "white")
meme("kitten.jpg", txt2, "meme3.jpg", col = clrs[1], shadow = clrs[2])

```








#Option 4: meme package II

This package is not being maintained, and the API to memecaptain for templates doesn't work. 

Looking for a new maintainer!
https://github.com/leeper/meme


memery package: 

note also need showtext and sysfonts packages






#Mario

https://github.com/rasmusab/beepr
```{r}

library(beepr)

beep(8)
```

"ping"
"coin"
"fanfare"
"complete"
"treasure"
"ready"
"shotgun"
"mario"
"wilhelm"
"facebook"
"sword"

#Messages

devtools::install_github("gaborcsardi/praise")

```{r}
library(praise
        )

praise()
```

#Goodshirt API to quotes from The Good Place
```{r}
devtools::install_github("adam-gruer/goodshirt")
```

```{r}
library(goodshirt)
library(cowsay)
library(magrittr)

soul_squad() 
```



#More